Automated Verification for Real-Time Systems using Implicit Clocks and an Extended Antimirov Algorithm

### 2022-04-12 paper/tv.tex
m

Having \timedEffects\ to be  the specification language, 
and the forward verifier to infer the program behaviors, 
we are interested 
in the following verification problem: 
Given a program \code{\mathcal{P}},
and a temporal specification \code{\effect^{\prime}}, does the inclusions 
\code{\effect^{\mathcal{P}} \CONTAIN \effect^{\prime}} holds? Typically, 
checking the inclusion/entailment between the concrete program effects \code{\effect^{\mathcal{P}}} and the valid traces \code{\effect^{\prime}} proves that: the program \code{\mathcal{P}} will never lead to unsafe traces which violate \code{\effect^{\prime}}.

Since the expressiveness of \timedEffects\ goes beyond 
finite-state automata, it is neither sufficient nor efficient to 
 translation them 
into Timed Automata and reply on the solving engines of Timed Automata.
Therefore we 
develop a novel TRS, 
which  is inspired by Antimirov and Mosses’ algorithm 
\cite{antimirov1995rewriting}\footnote{Antimirov and Mosses' 
algorithm was designed for deciding the inequalities of regular 
expressions based on an 
complete 
axiomatic algorithm of the algebra of regular sets.} but solving the 
language inclusions between more expressive \timedEffects.

@@

A TRS is a refutation method that normalizes expressions in such a way 
that checking their inclusion corresponds to an iterated process of 
checking the inclusion of their \emph{partial derivatives} 
\cite{antimirov1995partial}. 
Works based on such a TRS \cite{song2020automated,antimirov1995rewriting,almeida2009antimirov,keil2014symbolic,hovland2012inclusion}  show its feasibility and suggest that this method is a better average-case algorithm than those based on the comparison of automata.

@@

{
\begin{figure}[!ht]
    %  \vspace{-4mm}
     \begin{minipage}[c]{\columnwidth}
         \centering
         {\small
         \begin{enumerate}
\item \lstinline|void addOneSugar() {| \textcolor{mGray}{\footnotesize 
\quad \emph{// initialize the effects state using the function precondition \code{\effect_{pre}^{addOneSugar(n)}}}} \\
\textcolor{darklavender}{\{\code{\effect_C {=}\effect_{pre}^{addOneSugar(n)} =  true \wedge  \_^\star \} }} 
\quad \siderule{\scriptsize[FV\text{-}Meth] } \\

\item ~\qquad \lstinline|timeout ((), 1);}| \\
\textcolor{darklavender}{\code{\effect_C^\prime {=} t_0{>}1   \wedge \_^\star \cdot \epsilon \mysharp t_0  }} 
\quad \siderule {\scriptsize [FV\text{-}Timeout]}
\item 
\textcolor{darkred}{\code{
%\code{(n{=}0 \wedge \anyevent{Done})\ \vee\ }\code{ (n  \neq 0  \wedge \anyevent{Send}\cdot \effect_{post}^{addNSugar(n-1)}) } 
\effect_C^\prime \CONTAIN \effect_{pre}^{addOneSugar(n)} \cdot \effect_{post}^{addOneSugar(n)} \Leftrightarrow  }} 
 %\textcolor{mGray}{  \emph{(-- check postcondition --) }}
 \textcolor{darkred}{\code{\code{\code{t_0{>}1   \wedge \epsilon \mysharp t_0}
 \CONTAIN t{>}1   \wedge \epsilon \mysharp t }}}
 \quad \textcolor{mGray}{\footnotesize  \emph{// TRS: postcondition checked }}
 \\ 
%ens: t>1 /\ emp#t */ { 
  \noindent\rule{0.9\columnwidth}{0.4pt}
~\\
\item \lstinline|void addNSugar (int n) {| \textcolor{mGray}{\footnotesize 
\quad \emph{// initialize the effects state using the function precondition \code{\effect_{pre}^{addNSugar(n)}}.}} \\
     \textcolor{darklavender}{\{\code{\effect_C {=}\effect_{pre}^{addNSugar(n)} =  true \wedge  \_^\star \} }} 
      \quad \siderule{\scriptsize[FV\text{-}Meth] } \\
     \item ~\qquad \lstinline|if (n == 0) {| \\
     \textcolor{darklavender}{\code{\{ n{=}0 \wedge  \_^\star \}  }} 
     \quad \siderule{\scriptsize [FV\text{-}If\text{-}Else]}
      \item ~\qquad~\qquad \lstinline|event ["Sugar"];} |  \\
     \textcolor{darklavender}{\code{\{n{=}0 \wedge   \_^\star \cdot Sugar\} }} 
     \quad \siderule{\scriptsize [FV\text{-}Event]}
     \item 
     ~\qquad \lstinline|else {| \\
     \textcolor{darklavender}{\code{\{ n  {\neq} 0 \wedge   \_^\star \}  }} 
     \quad \siderule{\scriptsize [FV\text{-}If\text{-}Else]}
    \item 
     ~\qquad~\qquad \lstinline|addOneSugar();| \\
     \textcolor{darklavender}{\code{\{n  {\neq} 0 \wedge  t{>}1  \wedge \_^\star \cdot \epsilon \mysharp t  }\}} 
     \quad \siderule {\scriptsize [FV\text{-}Call]}
     \item 
     ~\qquad~\qquad \lstinline|addNSugar (n-1);}}|  \\
     \textcolor{huntergreen}{\code{n  {\neq} 0   \wedge t{>}1  \wedge \_^\star \cdot \epsilon \mysharp t   \CONTAIN \effect_{pre}^{addNSugar(n\text{-}1)} }}
      \quad \textcolor{mGray}{\footnotesize  \emph{// TRS: precondition checked.}}
\\
     \textcolor{darklavender}{\code{\{n  {\neq} 0  \wedge t{>}1  \wedge \_^\star 
     \cdot \epsilon \mysharp t \cdot \effect_{post}^{addNSugar(n\text{-}1)} }\}} 
     \quad \siderule {\scriptsize [FV\text{-}Call]}
      \item \textcolor{darklavender}{\code{\effect_C^\prime {=} (n{=}0 \wedge  \_^\star \cdot Sugar)\ \vee\ }
      \code{ (n  {\neq} 0  \wedge t{>}1  \wedge \_^\star \cdot \epsilon \mysharp t \cdot \effect_{post}^{addNSugar(n\text{-}1)} ) }} 
      \quad \siderule{\scriptsize [FV\text{-}If\text{-}Else]}
      %\quad \siderule {\scriptsize [Normalization]}
      \\
       \item 
       %\textcolor{mGray}{  \emph{(-TRS: check the  postcondition; Succeed, cf. \autoref{tab:rewriting_tree_send}-) }}\\
       \textcolor{darkred}{\code{
       %\code{(n{=}0 \wedge \anyevent{Done})\ \vee\ }\code{ (n  \neq 0  \wedge \anyevent{Send}\cdot \effect_{post}^{addNSugar(n-1)}) } 
       \effect_C^\prime \CONTAIN \effect_{pre}^{addNSugar(n)} \cdot \effect_{post}^{addNSugar(n)} \Leftrightarrow  }}  
       \quad \textcolor{mGray}{\footnotesize  \emph{// TRS: postcondition checked, cf. \autoref{tab:rewriting_tree_send}. }}
        \\ 
        \textcolor{darkred}{\code{\code{\code{(n{=}0 \wedge Sugar)\ \vee\ }
        \code{ (n  {\neq} 0  \wedge  t{>}1  \wedge \epsilon \mysharp t \cdot \effect_{post}^{addNSugar(n\text{-}1)}) } \CONTAIN \effect_{post}^{addNSugar(n)}}}}\\

@@

The effects states (1) and (4) are obtained by initializing 
\code{\effect_C} from the precondition, by the \code{[FV\text{-}Meth]} rule. 
The effects states (5), (7), and (10) are obtained by  
\code{[FV\text{-}If\text{-}Else]}, which adds the constraints 
from the conditionals into the current effects state, 
and unions the effects accumulated from two branches in the end. 
The effects states (6) is obtained by \code{[FV\text{-}Event]}, 
which concatenates the triggered singleton event to the 
end of the current effects state. 
The intermediate effects states of (8) and (9) are obtained by \code{[FV\text{-}Call]}. 
Before each function call, it invokes the TRS to check whether the current effects state 
satisfies the precondition of the callee function. 
If it is not satisfied, the verification fails; otherwise, 
it concatenates the callee's postcondition to the current 
effects state. (We omitted the precondition check for (8) here.)
The effects state (2) is obtained by \code{[FV\text{-}Timeout]}, 
which adds a lower time-bound to the trace. 
After these states transformations, steps (3) and (11) check the 
satisfiability of the inferred effects against the declared 
postcondition by invoking the TRS.

@@

\subsection{The TRS}
Our TRS is obligated to check the inclusions between \timedEffects, which is an extension of Antimirov and Mosses's algorithm. The rewriting system in {\cite{antimirov1995rewriting}  
%a TRS 
%for deciding the inequalities of regular expressions (REs), based on a complete axiomatic algorithm of the algebra of regular sets. 
%This method is shown to be a better average-case algorithm than those based on the comparison of minimal deterministic finite automatons (DFAs).}
%Basically, 
decides inequalities of regular expressions (REs) through an iterated process of checking the inequalities of their \emph{partial derivatives} \cite{antimirov1995partial}. There are two basic rules: 
\code{[DISPROVE]}, which infers false from trivially inconsistent inequalities; and  
\code{[UNFOLD]}, which applies \defref{RegularInclusion} to generate new inequalities.

Given \code{\Sigma} is the whole set of the alphabet, 
\code{D_{\anyevent{A}}(r)} is the partial derivative of \code{r} w.r.t the signal \code{\anyevent{A}}.

@@

Similarly, we defined the \defref{Inclusion} for unfolding the inclusions  between \timedEffects, where \code{D_{I\mysharp  t}(\effect)} is the partial derivative of \code{\effect} w.r.t the event \code{I} and time bound \code{t}.

\begin{definition}[\timedEffects Inclusion]\label{Inclusion}  %Let \code{\varrho} be the signal set. 
For \timedEffects \code{\effect_1 } and \code{\effect_2}, 
\code{\effect_1  \CONTAIN \effect_2 \Leftrightarrow \forall I. \forall t {\geq} 0.\ D_{I\mysharp  t}(\effect_1)  \CONTAIN D_{I\mysharp  t}(\effect_2)}.
\end{definition}
%\in fst(\effect_1)

@@

Next, we continue with the step (9) in \figref{fig:forward_example}, to 
demonstrate how the TRS handles arithmetic constraints and dependent values. 
%We use the postcondition proving for function \code{main} as an example to briefly demonstrate the rewriting process. 
As shown in \tabref{tab:rewriting_tree_send}, it automatically proves that the inferred effects of {\ttfamily{main}}
 satisfy the declared postcondition. 
%property \code{\effect_1  {=} 0{\leq} t {<}3 : \_\cdot(\{Cook\}\mysharp  t)\cdot\_^\star}, 
%where \code{\effect_1} simply indicates that the signal \anyevent{Cook} needs to happen at the second event, and takes no more than \code{3} time units after the first event has completed; and \code{\_^\star} means we do not care the rest of the traces. 
We mark the rewriting rules (cf. \secref{sec:Entailment_Prover}) in \textcolor{mGray}{[gray]}.

@@

%\vspace{-1mm}
\begin{adjustbox}{width=1\textwidth}
 \Large\begin{tabular}[t]{l}
  \hline\\
{

\begin{prooftree}
\Hypo{
  \code{\siderule{[Prove]}}
}

\Infer[dashed]1[]{ \code{ n{=}0 \wedge \epsilon 
\CONTAIN t_r{\geq}0 \wedge \epsilon \mysharp t_r}}

\Infer[dashed]1[]{ \code{ n{=}0 \wedge Sugar
\CONTAIN t_r{\geq}0 \wedge Sugar \mysharp t_r}}

\Hypo{
  \code{\textcolor {darkred}{  t{>}1 {\wedge} t_l{\geq}(n\text{-}1) 
   {\wedge}  t_r{=}t_r^1 {+}t {\wedge}  t_l{=}t_r^1  \Rightarrow t_r{\geq}n
}  } 
\code{\siderule{[Prove]}}
 }

 \Infer[dashed]1[]{ \code{ n  {\neq} 0  {\wedge}  t{>}1 {\wedge} t_l{\geq}(n\text{-}1)  \wedge 
 \epsilon
\CONTAIN t_r{\geq}n {\wedge}  t_r{=}t_r^1 {+}t {\wedge}  t_l{=}t_r^1 
\wedge \epsilon}}

 \Infer[dashed]1[]{ \code{ n  {\neq} 0  {\wedge}  t{>}1 {\wedge} t_l{\geq}(n\text{-}1)  \wedge 
 Sugar \mysharp t_l
\CONTAIN t_r{\geq}n {\wedge}  t_r{=}t_r^1 {+}t
\wedge Sugar \mysharp t_r^1}}

 \Infer[dashed]1[]{ \code{ n  {\neq} 0  {\wedge}  t{>}1 {\wedge} t_l{\geq}(n\text{-}1)  \wedge \epsilon \mysharp t \cdot 
 Sugar \mysharp t_l
\CONTAIN t_r{\geq}n \wedge Sugar \mysharp t_r}}

\Infer[dashed]2[]{\code{(n{=}0 \wedge Sugar)\ \vee\ }
\code{ (n  {\neq} 0  \wedge  t{>}1 \wedge t_l{\geq}(n\text{-}1)  \wedge \epsilon \mysharp t \cdot 
 Sugar \mysharp t_l) } 
\CONTAIN t_r{\geq}n \wedge Sugar \mysharp t_r  }

\Infer[dashed]1[{\siderule{\textcircled{1}[RENAME]}}]{\code{(n{=}0 \wedge Sugar)\ \vee\ }
\code{ (n  {\neq} 0  \wedge  t{>}1  \wedge \epsilon \mysharp t \cdot \effect_{post}^{addNSugar(n\text{-}1)}) } 
\CONTAIN \effect_{post}^{addNSugar(n)}  }
\end{prooftree}}
\\~\\

@@

Note that event \code{\{Prep\}} entails \code{\_} because the former contains more constraints. We formally define the subsumption for time instances in \defref{Subsumption}.
Intuitively, we use \code{[DISPROVE]} wherever the left-hand side (LHS) is \emph{nullable}\footnote{If the event sequence is possibly empty, i.e. contains \code{\empt}, we call it nullable, formally defined in \defref{Nullable}.} while the right-hand side (RHS) is not. 
\code{[DISPROVE]} is the heuristic refutation step to disprove the inclusion early, improving the verification efficiency.

@@

%(\code{\{Go\} \Rightarrow \_})
%(\code{\{Ready\} \Rightarrow \_}, \code{t_L^2 \Rightarrow true})
Termination is guaranteed because the set of derivatives to be considered is finite, and possible cycles are detected using \emph{memorization} \cite{brotherston2005cyclic} (cf. \tabref{tab:rewriting_tree_case_study_finit_infinit}).

@@

Moreover, our \timedEffects also draws similarities to Synchronous Kleene Algebra (SKA) \cite{prisacariu2010synchronous}. 
%Antimirov and Mosses' algorithm \cite{antimirov1995rewriting} was designed for deciding the inclusion of regular expressions.   
Kleene algebra (KA) is a decades-old sound and complete equational theory of regular expressions. Among many extensions of KA,
 %timed synchronous 
  SKA is KA extended with a synchrony combinator for actions. In particularly, SKA's \emph{demanding relation} can be reflected by our \emph{instances subsumption} (\defref{Subsumption}), which contributes to the inductive unfolding process. 
Yet our timed effects further capture the time bounds constraints by adding the operator \code{\mysharp }, adapting to real-time system modeling and verification, which is not covered by any existing KA variants/extensions.

>>>>

Having \timedEffects\ to be  the specification language, 
and the forward verifier to infer the program behaviors, 
we are interested 
in the following verification problem: 
Given a program \code{\mathcal{P}},
and a temporal specification \code{\effect^{\prime}}, does the inclusions 
\code{\effect^{\mathcal{P}} \CONTAIN \effect^{\prime}} holds\footnote{The 
inclusion relation $\CONTAIN$ is formally defined in \defref{Inclusion}.}? Typically, 
checking the inclusion/entailment between the concrete program effects \code{\effect^{\mathcal{P}}} and the valid traces \code{\effect^{\prime}} proves that: the program \code{\mathcal{P}} will never lead to unsafe traces which violate \code{\effect^{\prime}}.

Since the expressiveness of \timedEffects\ goes beyond 
finite-state automata, it is neither sufficient nor efficient to 
 translation them 
into Timed Automata and reply on the solving engines of Timed Automata.
Therefore we 
develop a novel TRS, 
which  is inspired by Antimirov and Mosses’ algorithm\footnote{Antimirov and Mosses' 
algorithm was designed for deciding the inequalities of regular 
expressions based on an 
complete 
axiomatic algorithm of the algebra of regular sets.} \cite{DBLP:journals/tcs/AntimirovM95} but solving the 
language inclusions between more expressive \timedEffects.

@@

A TRS is a refutation method that normalizes expressions in such a way 
that checking their inclusion corresponds to an iterated process of 
checking the inclusion of their \emph{partial derivatives} 
\cite{antimirov1995partial}. 
Works based on such a TRS \cite{song2020automated,DBLP:journals/tcs/AntimirovM95,almeida2009antimirov,keil2014symbolic,hovland2012inclusion}  show its feasibility and suggest that this method is a better average-case algorithm than those based on the comparison of automata.

@@

{
\begin{figure}[!ht]
    %  \vspace{-4mm}
     \begin{minipage}[c]{\columnwidth}
         \centering
         {%\small
         \begin{enumerate}
\item \lstinline|void addOneSugar() {| \textcolor{mGray}{\footnotesize 
\quad \emph{// initialize the effects state using the function precondition \code{\effect_{pre}^{addOneSugar(n)}}}} \\
\textcolor{darklavender}{\{\code{\effect_C {=}\effect_{pre}^{addOneSugar(n)} =  true \wedge  \_^\star \} }} 
\quad \siderule{\scriptsize[FV\text{-}Meth] } \\

\item ~\qquad \lstinline|timeout ((), 1);}| \\
\textcolor{darklavender}{\code{\effect_C^\prime {=} t_0{>}1   \wedge \_^\star \cdot \epsilon \mysharp t_0  }} 
\quad \siderule {\scriptsize [FV\text{-}Timeout]}
\item 
\textcolor{darkred}{\code{
%\code{(n{=}0 \wedge \anyevent{Done})\ \vee\ }\code{ (n  \neq 0  \wedge \anyevent{Send}\cdot \effect_{post}^{addNSugar(n-1)}) } 
\effect_C^\prime \CONTAIN \effect_{pre}^{addOneSugar(n)} \cdot \effect_{post}^{addOneSugar(n)} \Leftrightarrow  }} 
 %\textcolor{mGray}{  \emph{(-- check postcondition --) }}
 \textcolor{darkred}{\code{\code{\code{t_0{>}1   \wedge \epsilon \mysharp t_0}
 \CONTAIN t{>}1   \wedge \epsilon \mysharp t }}}
 \quad \textcolor{mGray}{\footnotesize  \emph{// TRS: postcondition checked }}
 \\ 
%ens: t>1 /\ emp#t */ { 
  \noindent\rule{0.92\columnwidth}{0.4pt}
~\\
\item \lstinline|void addNSugar (int n) {| \textcolor{mGray}{\footnotesize 
\quad \emph{// initialize the effects state using the function precondition \code{\effect_{pre}^{addNSugar(n)}}.}} \\
     \textcolor{darklavender}{\{\code{\effect_C {=}\effect_{pre}^{addNSugar(n)} =  true \wedge  \_^\star \} }} 
      \quad \siderule{\scriptsize[FV\text{-}Meth] } \\
     \item ~\qquad \lstinline|if (n == 0) {| \\
     \textcolor{darklavender}{\code{\{ n{=}0 \wedge  \_^\star \}  }} 
     \quad \siderule{\scriptsize [FV\text{-}If\text{-}Else]}
      \item ~\qquad~\qquad \lstinline|event ["Sugar"];} |  \\
     \textcolor{darklavender}{\code{\{n{=}0 \wedge   \_^\star \cdot Sugar\} }} 
     \quad \siderule{\scriptsize [FV\text{-}Event]}
     \item 
     ~\qquad \lstinline|else {| \\
     \textcolor{darklavender}{\code{\{ n  {\neq} 0 \wedge   \_^\star \}  }} 
     \quad \siderule{\scriptsize [FV\text{-}If\text{-}Else]}
    \item 
     ~\qquad~\qquad \lstinline|addOneSugar();| \\
     \textcolor{darklavender}{\code{\{n  {\neq} 0 \wedge  t{>}1  \wedge \_^\star \cdot \epsilon \mysharp t  }\}} 
     \quad \siderule {\scriptsize [FV\text{-}Call]}
     \item 
     ~\qquad~\qquad \lstinline|addNSugar (n-1);}}|  \\
     \textcolor{huntergreen}{\code{n  {\neq} 0   \wedge t{>}1  \wedge \_^\star \cdot \epsilon \mysharp t   \CONTAIN \effect_{pre}^{addNSugar(n\text{-}1)} }}
      \quad \textcolor{mGray}{\footnotesize  \emph{// TRS: precondition checked.}}
\\
     \textcolor{darklavender}{\code{\{n  {\neq} 0  \wedge t{>}1  \wedge \_^\star 
     \cdot \epsilon \mysharp t \cdot \effect_{post}^{addNSugar(n\text{-}1)} }\}} 
     \quad \siderule {\scriptsize [FV\text{-}Call]}
      \item \textcolor{darklavender}{\code{\effect_C^\prime {=} (n{=}0 \wedge  \_^\star \cdot Sugar)\ \vee\ }
      \code{ (n  {\neq} 0  \wedge t{>}1  \wedge \_^\star \cdot \epsilon \mysharp t \cdot \effect_{post}^{addNSugar(n\text{-}1)} ) }} 
      \quad \siderule{\scriptsize [FV\text{-}If\text{-}Else]}
      %\quad \siderule {\scriptsize [Normalization]}
      \\
       \item 
       %\textcolor{mGray}{  \emph{(-TRS: check the  postcondition; Succeed, cf. \autoref{tab:rewriting_tree_send}-) }}\\
       \textcolor{darkred}{\code{
       %\code{(n{=}0 \wedge \anyevent{Done})\ \vee\ }\code{ (n  \neq 0  \wedge \anyevent{Send}\cdot \effect_{post}^{addNSugar(n-1)}) } 
       \effect_C^\prime \CONTAIN \effect_{pre}^{addNSugar(n)} \cdot \effect_{post}^{addNSugar(n)} \Leftrightarrow  }}  
       \quad \textcolor{mGray}{\footnotesize  \emph{// TRS: postcondition checked, cf. \autoref{tab:rewriting_tree_send}. }}
        \\ 
        \textcolor{darkred}{\code{\code{\code{(n{=}0 \wedge Sugar)\ \vee\ }
        \code{ (n  {\neq} 0  \wedge  t{>}1  \wedge \epsilon \mysharp t \cdot \effect_{post}^{addNSugar(n\text{-}1)}) } \CONTAIN \effect_{post}^{addNSugar(n)}}}}\\

@@

The effects states (1) and (4) are obtained by initializing 
\code{\effect_C} from the precondition, by the \code{[FV\text{-}Meth]} rule. 
The effects states (5), (7), and (10) are obtained by  
\code{[FV\text{-}If\text{-}Else]}, which adds the constraints 
from the conditionals into the current effects state, 
and unions the effects accumulated from two branches in the end. 
The effects states (6) is obtained by \code{[FV\text{-}Event]}, 
which concatenates the triggered singleton event to the 
end of the current effects state.

The intermediate effects states of (8) and (9) are obtained by \code{[FV\text{-}Call]}. 
Before each function call, it invokes the TRS to check whether the current effects state 
satisfies the precondition of the callee function. 
If it is not satisfied, the verification fails; otherwise, 
it concatenates the callee's postcondition to the current 
effects state (the precondition check for step (8) is omitted here).

The effects state (2) is obtained by \code{[FV\text{-}Timeout]}, 
which adds a lower time-bound to the trace. 
After these states transformations, steps (3) and (11) check the 
satisfiability of the inferred effects against the declared 
postcondition by invoking the TRS.

@@

\subsection{The TRS}

Our TRS is 
%obligated to check the inclusions between \effectNameSyncEffs, which is 
an extension of Antimirov and Mosses's algorithm. The rewriting system in {\cite{DBLP:journals/tcs/AntimirovM95}  
decides inequalities of regular expressions (REs) through an iterated process of checking the inequalities of their 
\emph{partial derivatives} \cite{antimirov1995partial}. There are two basic rules: 
$\codeme{[DISPROVE]}$, which infers false from trivially inconsistent inequalities; and  
$\codeme{[UNFOLD]}$, which applies \autoref{RegularInclusion} to generate new inequalities.
In detail, given \code{\Sigma} is the whole set of the alphabet, 
\code{D_{\anyevent{A}}(r)} is the partial derivative of \code{r} w.r.t the event \code{\anyevent{A}}.

@@

\begin{definition}[\timedEffects\ Inclusion]\label{Inclusion}  %Let \code{\varrho} be the signal set. 
For \timedEffects\ \code{\effect_1 } and \code{\effect_2}, 
\code{\effect_1 { \CONTAIN} \effect_2 {\Leftrightarrow} \forall \anyevent{A}. \forall t {\geq} 0.\ D_{\anyevent{A} \mysharp  t}(\effect_1)  
{\CONTAIN} D_{\anyevent{A} \mysharp  t}(\effect_2)}.
\end{definition}
%\in fst(\effect_1)

Similarly, we defined the \defref{Inclusion} for unfolding the inclusions  
between \timedEffects, where \code{D_{\anyevent{A}\mysharp  t}(\effect)} 
is the partial derivative of \code{\effect} w.r.t the event 
\anyevent{A} and the time variable \code{t}.

@@

Next, we continue with the step (11) in \figref{fig:forward_example}, to 
demonstrate how the TRS handles arithmetic constraints and dependent values. 
%We use the postcondition proving for function \code{main} as an example to briefly demonstrate the rewriting process. 
As shown in \tabref{tab:rewriting_tree_send}, it automatically proves that the inferred effects of {\ttfamily{main}}
 satisfy the declared postcondition. 
%property \code{\effect_1  {=} 0{\leq} t {<}3 : \_\cdot(\{Cook\}\mysharp  t)\cdot\_^\star}, 
%where \code{\effect_1} simply indicates that the signal \anyevent{Cook} needs to happen at the second event, and takes no more than \code{3} time units after the first event has completed; and \code{\_^\star} means we do not care the rest of the traces. 
We mark the rewriting rules (cf. \secref{sec:Entailment_Prover}) in \textcolor{mGray}{[gray]}.

@@

  \code{(I):}\quad

  {
\begin{prooftree}
\Hypo{
  \code{\textcircled{4}\siderule{[\codeme{PROVE}]}}
}

\Infer[dashed]1[]{ \code{\textcolor {darkred}{n{=}0} \wedge \epsilon 
\CONTAIN \textcolor {darkred}{t_r{\geq}0} \wedge \epsilon \mysharp t_r}}

\Infer[dashed]1[{\textcircled{3}\siderule{[\codeme{UNFOLD}]}} \textcolor{blue}{\code{\pi_u : true}}]{ \code{ \textcolor {darkred}{n{=}0} \wedge Sugar
\CONTAIN \textcolor {darkred}{t_r{\geq}0} \wedge Sugar \mysharp t_r}}

\Hypo{\code{(II)}}

\Infer[dashed]2[{\textcircled{2}\siderule{[\codeme{LHS\text{-}OR}]}}]{\code{(\textcolor {darkred}{n{=}0} \wedge Sugar)\ \vee\ }
\code{ (\textcolor {darkred}{n  {\neq} 0  \wedge  t{>}1 \wedge t_l{\geq}(n\text{-}1)}  \wedge \epsilon \mysharp t \cdot 
 Sugar \mysharp t_l) } 
\CONTAIN \textcolor {darkred}{t_r{\geq}n} \wedge Sugar \mysharp t_r  }

\Infer[dashed]1[{\textcircled{1}\siderule{[\codeme{RENAME}]}}]{\code{(\textcolor {darkred}{n{=}0} \wedge Sugar)\ \vee\ }
\code{ (\textcolor {darkred}{n  {\neq} 0  \wedge  t{>}1}  \wedge \epsilon \mysharp t \cdot \effect_{post}^{addNSugar(n\text{-}1)}) } 
\CONTAIN \effect_{post}^{addNSugar(n)}  }
\end{prooftree}}
\\~\\

\hline \\
\code{(II):} \quad

{\begin{prooftree}
  \Hypo{
  \code{\textcolor {darkred}{  t{>}1 \wedge t_l{\geq}(n\text{-}1) 
   \wedge  \textcolor{blue}{t_r{=}t_r^1 {+}t \wedge  t_l{=}t_r^1}  \Rightarrow t_r{\geq}n
}  } 
 }

 \Infer[dashed]1[{\textcircled{7}\siderule{[\codeme{PROVE}]}}]{ \code{ \textcolor {darkred}{n  {\neq} 0  \wedge  t{>}1 \wedge t_l{\geq}(n\text{-}1)}  \wedge 
 \epsilon
\CONTAIN \textcolor {darkred}{t_r{\geq}n} 
\wedge \epsilon}}

 \Infer[dashed]1[{\textcircled{6}\siderule{[\codeme{UNFOLD}]}} \textcolor{blue}{\code{\pi_u :  (t_r{=}t_r^1 {+}t \wedge  t_l{=}t_r^1)}}]
 { \code{ \textcolor {darkred}{n  {\neq} 0  \wedge  t{>}1 \wedge t_l{\geq}(n\text{-}1)}  \wedge 
 Sugar \mysharp t_l
\CONTAIN \textcolor {darkred}{t_r{\geq}n} 
\wedge Sugar \mysharp t_r^1}}

 \Infer[dashed]1[{\textcircled{5}\siderule{[\codeme{UNFOLD}]}} \textcolor{blue}{\code{\pi_u :  (t_r{=}t_r^1 {+}t)}}]
 { \code{ \textcolor {darkred}{n  {\neq} 0  \wedge  t{>}1 \wedge t_l{\geq}(n\text{-}1) } \wedge \epsilon \mysharp t \cdot 
 Sugar \mysharp t_l
\CONTAIN \textcolor {darkred}{t_r{\geq}n} \wedge Sugar \mysharp t_r}}

\end{prooftree}
}

@@

@@

%(\code{\{Go\} \Rightarrow \_})
%(\code{\{Ready\} \Rightarrow \_}, \code{t_L^2 \Rightarrow true})
Termination is guaranteed because the set of derivatives to be considered is finite, and possible cycles are detected using \emph{memorization} \cite{brotherston2005cyclic}. %(cf. \tabref{tab:rewriting_tree_case_study_finit_infinit}).

@@

Moreover, our \timedEffects also draws similarities to Synchronous Kleene Algebra (SKA) \cite{prisacariu2010synchronous}. 
%Antimirov and Mosses' algorithm \cite{DBLP:journals/tcs/AntimirovM95} was designed for deciding the inclusion of regular expressions.   
Kleene algebra (KA) is a decades-old sound and complete equational theory of regular expressions. Among many extensions of KA,
 %timed synchronous 
  SKA is KA extended with a synchrony combinator for actions. In particularly, SKA's \emph{demanding relation} can be reflected by our \emph{instances subsumption} (\defref{Subsumption}), which contributes to the inductive unfolding process. 
Yet our timed effects further capture the time bounds constraints by adding the operator \code{\mysharp }, adapting to real-time system modeling and verification, which is not covered by any existing KA variants/extensions.
